Lyman-$\alpha$ photons through rotating outflows

### 2018-08-06 paper/paper.tex
typo

In this paper we explore, for the first time in the literature,
the results of a model for the emergent \lya line from rotating
outflows. 
We use a semi-analytic model, first presented in \citep{Garavito14}, that
to capture the main effects of rotation and confront it against
results from Monte-Carlo radiative transfer simulations. 
The semi-analytic model only takes into account the Doppler shift computed
as product of quantities at the surface of last scattering, namely
$\vec{v}_{\rm rot}\cdot \hatk$, where $\vec{v}_{\rm rot}$ is the
velocity due to rotation and \hatk is the direction of the photon's
propagation.

>>>>

In this paper we explore, for the first time in the literature,
the results of a model for the emergent \lya line from rotating
outflows. 
We use a semi-analytic model, first presented in \citep{Garavito14}, 
to capture the main effects of rotation and confront it against
results from Monte-Carlo radiative transfer simulations. 
The semi-analytic model only takes into account the Doppler shift computed
as product of quantities at the surface of last scattering, namely
$\vec{v}_{\rm rot}\cdot \hatk$, where $\vec{v}_{\rm rot}$ is the
velocity due to rotation and \hatk is the direction of the photon's
propagation.
